Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-11 doc/main_jfm.tex
updates
few small changes

\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. A second-order Adam-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eqn:REPULforce} and
torque~\eqref{eqn:REPULtorque}, particle collisions are avoided even
when using a relatively large time step.

@@

In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
the vesicle is about $8.5$ length units.
The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations. 
This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$. In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model. This implies that a local energy minimum and the equilibrium configuration are 
nearly attained. 
The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run. The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations. The pressure inside the permeable Janus-vesicle decreases as expected.

@@

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
interfacial tension $\gamma=4.1$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the corresponding 
time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
$\kappa=8.51$ kT.

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
\begin{align}
  \chi = \dot\gamma \frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.

@@

The intermonolayer friction coefficient of the Janus-vesicle is calculated from the ratio of friction force and the 
slip velocity. This quantity is given by 
\begin{equation}
b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_{\Sigma_M} R \dot\theta dS}.
\end{equation}
%
where $v^\parallel$ represents the tangential velocity at the midplane and $\Sigma_M$ the curve determined by the midplane.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c}
\hline\hline                    
Case $i$ & $\chi_i$ & $b_i$\\
\hline 
1 & 0.020 &  5.1648  \\
2 & 0.025 &  5.2027  \\ 
3 & 0.050 &  5.1944   \\ [1ex]
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

To prove \eqref{eq:recipforcetorque}, write
\begin{align*}
  {\bf T}
  &=
  \sigma[u_p,u_p]
  +(\sigma[u_p,v_p]
  +\sigma[v_p,u_p])
  +\sigma[v_p,v_p] \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where
\[
\sigma[u,v]
= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \otimes \nabla v.
\]
\begin{lemma}
  \label{eq:stress_div_lemma}
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot (x \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
  \end{equation}
\end{lemma}
\begin{proof}
  Observe that
  \begin{align*}
    (\nabla \cdot {\bf T})_j &=
    \nabla_k   T_{jk} \\
    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
    - 2 \nabla_j u \nabla_{kk}^2 u )\\
    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u .
  \end{align*}
  However, $-\rho^2 \Delta u + u = 0$ and so we get $\nabla \cdot {\bf T} = 0.$
  Furthermore,
  \begin{align*}
    (\nabla \cdot (x\times {\bf T} ))_j
    &= (\nabla \cdot ({\bf X} {\bf T} ))_j
    = \nabla_k (X_{jl} T_{lk})
    = \nabla_k (\epsilon_{jml}x_m T_{lk})\\
    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
  \end{align*}
  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
  $\nabla \cdot (x \times {\bf T}) = 0$ as well.

>>>>

\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. A second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eqn:REPULforce} and
torque~\eqref{eqn:REPULtorque}, particle collisions are avoided even
when using a relatively large time step.

@@

In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
the vesicle is about $8$ length units.
The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations. 
This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$. In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model. This implies that a local energy minimum and the equilibrium configuration are 
nearly attained. 
The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run. The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations. The pressure inside the permeable Janus-vesicle decreases as expected.

@@

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
interfacial tension $\gamma=4.11$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP. With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_B$T.
%
For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ 
is the shear rate.

%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
%\begin{align}
%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
%\end{align}
%%
%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.

@@

The intermonolayer friction coefficient of the Janus-vesicle is calculated from the ratio of friction force and the 
slip velocity. This quantity is given by 
\begin{equation}
b = \frac{F_f}{v^\parallel} = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS}.
\end{equation}
%
where $v^\parallel$ represents the tangential velocity at the midplane and $\Sigma_M$ the curve determined by the midplane.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
\hline                    
$\dot\gamma$ (ns$^{-1}$) & 0.0020 & 0.0025 & 0.0030 & 0.0035 & 0.0040 & 0.0045 & 0.0050\\
\hline 
$F_{f}$ (pN nm$^{-1}$)           &  &  &  &  &  &  &   \\[1ex]
$\dot\theta$ (ns$^{-1}$)           &  &  &  &  &  &  & \\ [1ex]
$b$ (pN$\cdot$ns nm$^{-2}$)   &  &  &  &  &  &  & \\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

To prove \eqref{eq:recipforcetorque}, write
\begin{align*}
  {\bf T}
  &=
  \sigma[u_p,u_p]
  +(\sigma[u_p,v_p]
  +\sigma[v_p,u_p])
  +\sigma[v_p,v_p] \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where
\[
\sigma[u,v]
= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \otimes \nabla v.
\]
\begin{lemma}
  \label{eq:stress_div_lemma}
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
  \end{equation}
\end{lemma}
\begin{proof}
  Observe that
  \begin{align*}
    (\nabla \cdot {\bf T})_j &=
    \nabla_k   T_{jk} \\
    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
    - 2 \nabla_j u \nabla_{kk}^2 u )\\
    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u .
  \end{align*}
  Since $-\rho^2 \Delta u + u = 0$, we have $\nabla \cdot {\bf T} = 0$.
  Furthermore,
  \begin{align*}
    (\nabla \cdot (x\times {\bf T} ))_j
    &= (\nabla \cdot ({\bf X} {\bf T} ))_j
    = \nabla_k (X_{jl} T_{lk})
    = \nabla_k (\epsilon_{jml}x_m T_{lk})\\
    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
  \end{align*}
  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
  $\nabla \cdot (x \times {\bf T}) = 0$ as well.
